---
title: "Multivariate Analysis Steps for Feature Matrix 2"
output: github_document
---

Author: Purva Kulkarni
Date: 11 July 2016

This documents contains code snippets to perform multivariate analysis performed on the feature matrix 2 obtained after preprocessed the MS peaklists (Code for preprocessing: `processPeaklists.R`. The preprocessing steps do contain steps perform alignment and calibration. The parameters for baseline correction and peak detection are fine tuned. 

Read the featureMatrix 2 from the .csv file, create column and row headers and view

```{r, echo=TRUE}
data <- read.csv("FeatureMatrix2.csv", header = TRUE)
data2 <- cbind(data$V1, data$V2, data$V3, data$V4, data$V5, data$V6, data$V7, data$V8, data$V9)
colnames(data2) <- c("JantAD801", "JantAD802", "JantAD803", "SerratiaPRI1", "SerratiaPRI2", "SerratiaPRI3", "TSBagar1", "TSBagar2", "TSBagar3")
temp1 <- c(data$X)
temp1 <- as.character(round(temp1, digits = 4))
rownames(data2) <- temp1
head(data2)
```

View pair wise scatter plots and their correlations

```{r, echo=TRUE}
panel.cor <- function(x, y, digits=2, prefix="", cex.cor) 
{
  usr <- par("usr"); on.exit(par(usr)) 
  par(usr = c(0, 1, 0, 1)) 
  r <- abs(cor(x, y)) 
  txt <- format(c(r, 0.123456789), digits=digits)[1] 
  txt <- paste(prefix, txt, sep="") 
  if(missing(cex.cor)) cex <- 0.8/strwidth(txt) 
  
  test <- cor.test(x,y) 
  # borrowed from printCoefmat
  Signif <- symnum(test$p.value, corr = FALSE, na = FALSE, 
                   cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
                   symbols = c("***", "**", "*", ".", " ")) 
  
  text(0.5, 0.5, txt, cex = cex * r) 
  text(.8, .8, Signif, cex=cex, col=2) 
}
pairs(data2, lower.panel=panel.smooth, upper.panel=panel.cor)
```

Visualize the contribution to the overall variance from individual mass values

```{r, echo = TRUE}
library(factoextra)
res.pca <- prcomp(data2,  scale = TRUE)
fviz_pca_ind(res.pca, col.ind="contrib") +
scale_color_gradient2(low="white", mid="blue",
high="red", midpoint=4)
```

Transform the `data2` matrix, convert the matrx to a `data.frame` and add a `Species` column to the this matrix. 

```{r, echo=TRUE}
data2Transformed <- t(data2)
Species <- c("JantAD80", "JantAD80", "JantAD80", "SerratiaPR", "SerratiaPR", "SerratiaPR", "TSBAgar", "TSBAgar", "TSBAgar")
data2Transformed <- as.data.frame(data2Transformed)
Species <- as.factor(Species)
data2Transformed <- cbind(data2Transformed, Species)
df <- data2Transformed[c(1:length(data2Transformed)-1)]
library(ggfortify)
autoplot(prcomp(df), data = data2Transformed, colour = 'Species', label  =TRUE, label.size = 3, loadings = TRUE, loadings.colour = 'black', loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = 'Navyblue')
summary(prcomp(df))
```

On performing correlation analysis, it still shows some amount of positive correlation amongst samples

```{r, echo=TRUE}
library(corrplot)
source("http://www.sthda.com/upload/rquery_cormat.r")
rquery.cormat(data2)
cor.data2 <- cor(data2)
corrplot(cor.data2, method = "number")
```


