---
title: "Multivariate Analysis Steps"
output: github_document
---

Author: Purva Kulkarni
Date: 7 July 2016

This documents contains code snippets to perform multivariate analysis performed on the feature matrix obtained after preprocessed the MS peaklists (Code for preprocessing: `processPeaklists.R`. 


Read the featureMatrix from the .csv file, create column and row headers and view
```{r, echo=TRUE}
data <- read.csv("FeatureMatrix.csv", header = TRUE)
data2 <- cbind(data$V1, data$V2, data$V3, data$V4, data$V5, data$V6, data$V7, data$V8, data$V9)
colnames(data2) <- c("Jant_AD80_1", "Jant_AD80_2", "Jant_AD80_3", "Serratia_PRI_1", "Serratia_PRI_2", "Serratia_PRI_3", "TSB-agar__1", "TSB-agar__2", "TSB-agar__3")
temp1 <- c(data$X)
temp1 <- as.character(round(temp1, digits = 4))
rownames(data2) <- temp1
head(data2)
```
View a matrix of pairwise scatter plots for the data 
```{r, echo=TRUE}
pairs(data2)
```


Perform PCA on the feature matrix and view the pca summary, scree plot and score plot

```{r, echo=TRUE}
data2.pca1 <- princomp(data2, scores = TRUE, cor = TRUE)
summary(data2.pca1)
library(factoextra)
fviz_screeplot(data2.pca1)
biplot(data2.pca1)
library(FactoMineR)
result <- PCA(data2)
```


Visualization of the variables on a factor map

```{r, echo=TRUE}
fviz_pca_var(data2.pca1)
```


Visualization of correlation plot for the different samples

```{r, echo=TRUE}
library(psych)
data2.cor1 <- cor(data2)
corPlot(data2.cor1)
```
